jstor: Parsing XML - Lessons From Writing a Package

### 2018-09-30 draft.Rmd
update draft
use long tack instead of two short ones

---
title: 'jstor: Parsing XML - Lessons From Writing a Package'
author: "Thomas Klebel"
date: "30 9 2018"
output: html_document
---

@@

This is the story of `jstor`, a package that I wrote over the last year and a
half. It is a story about learning how to parse XML efficiently and creating a
piece of software that others will find useful. The story has many twists, and
I would like to take you with me -- on a journey that has told me many lessons.

>>>>

---
title: 'jstor: Parsing XML - Lessons From Writing a Package'
author: "Thomas Klebel"
date: "30 9 2018"
output: 
  html_document:
    keep_md: true
---

@@

This is the story of `jstor`, a package that I wrote over the last year and a
half. It is a story about learning how to parse XML efficiently and creating a
piece of software that others will find useful. The story has many twists, and
I would like to take you with me – on a journey that has told me many lessons.
